method

### 2022-03-03 06_Paper/ER-ED/method.Rmd
added ER ED Design and cross referencing

The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...). <!-- Attention!add EK number, when approved --> 
Prior to testing, written informed consent will be obtained.
Participants will receive 30€ in total or course credit for participation.

@@

The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] will be used.
Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from @Bernecker2017.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] will be used.
To assess self-control, sum scores of the German versions of the following questionnaires will be used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) [@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
Attentional control will be assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires).

@@

*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021].
Participants will be told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
Every participant first will have the condition "active viewing-neutral" that serves as a baseline condition.
During this block, 20 neutral pictures will be presented.
Participants will be asked to "actively view all pictures and permit all emotions that may arise." 
In the second block, participants will actively view negative pictures.
During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants will be asked to "take the position of a non-involved observer, thinking about the picture in a neutral way." 
Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants will be told to "suppress their emotional facial expression." 
They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants will receive written instruction and complete a training session.
After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.

*Part two: ER effort discounting.* <br> In the second part, ER effort discounting will take place.
The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with a major change.
We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies with monetary values will be presented.
The order of the comparisons will be randomized.
Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option "1 EUR for strategy A or 1 EUR for strategy B".
The strategy that is not chosen will be assigned the value of 2 EUR.
From this point on, comparisons between strategies will follow the original COG-ED paradigm [@Westbrook2013].
Participants will be instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.

@@

>>>>

The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...). <!-- Attention!add EK number, when approved --> 
Prior to testing, written informed consent will be obtained.
Participants will receive 30 € in total or course credit for participation.

@@

The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] will be used.
Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from @Bernecker2017.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] will be used.
To assess self-control [@Paschke2016], sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) [@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
Attentional control will be assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires).

@@

*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure \@ref(fig:Design_ER-ED)), similar to paradigms previously used by our group [@Scheffel2021].
Participants will be told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
Every participant first will have the condition "active viewing-neutral" that serves as a baseline condition.
During this block, 20 neutral pictures will be presented.
Participants will be asked to "actively view all pictures and permit all emotions that may arise." 
In the second block, participants will actively view negative pictures.
During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants will be asked to "take the position of a non-involved observer, thinking about the picture in a neutral way." 
Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants will be told to "suppress their emotional facial expression." 
They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants will receive written instruction and complete a training session.
After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.

*Part two: ER effort discounting.* <br> In the second part, ER effort discounting will take place.
The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with a major change.
We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies with monetary values will be presented.
The order of the comparisons will be randomized.
Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option "1 € for strategy A or 1 € for strategy B".
The strategy that is not chosen will be assigned the value of 2 €.
From this point on, comparisons between strategies will follow the original COG-ED paradigm [@Westbrook2013].
Participants will be instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.

@@

```{r Design_ER-ED, echo = FALSE, message = FALSE, warning = FALSE, fig.cap="Block design of the paradigm. Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures. Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants. After, the discounting procedure takes place. All three regulation strategies are pairwise compared. Before the last block, participants can decide which regulation strategy they want to reapply. Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale."}
include_graphics(here("0g_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
```
